\cvsection{Experience}

\begin{cventries}

  \cventry
    {Ecuafranquicias}
    {Project Manager}
    {Quito, Ecuador}
    {Oct 2016 - present}
    {
      \begin{cvitems}
        \item {Automation of multiple internal processes using oﬀice automation tools and Excel to reduce in half the time needed to deliver the product to our clients while simultaneously detecting errors in the development stage and giving employees more autonomy to develop their daily tasks.}
        \item {While the processes automation improved a lot of things, it was not enough to maximize the performance of the employees, a system was needed. This system will use modern web technologies to gather, store, and manage information in an accessible way for our employees via the internet.}
        \item {Documentation of the operative and administrative processes of our clients.}
        \item {Implementation of email marketing campaigns using MailChimp to approximately 3000+ subscribers.}
        \item {An SEO strategy was put in place to improve local search results, it helped us reach the first positions in Google. This strategy consisted of a webpage redesign, webpage optimization, keyword research and analysis, content creation, webpage analytics.}
      \end{cvitems}
    }

    \cventry
      {Independent Work}
      {Web Developer}
      {Quito, Ecuador}
      {June 2017 - present}
      {
        \begin{cvitems}
          \item {Performed website design and development for clients in diverse fields such as consulting, non-profit organizations, and law firms using various CMS.}
          \item {Websites were designed with a focus on achieving maximum performance, faster loading times, mobile-friendly and optimized for SEO purposes.}
        \end{cvitems}
      }

  \cventry
    {Department of Energy and Mechanic Sciences - ESPE}
    {Research and Teaching Assistant of Computer-aided Design, Manufacture and Engineering subject (CAD, CAM, CAE)	}
    {Quito, Ecuador}
    {Nov. 2015 – Feb. 2016}
    {
      \begin{cvitems}
        \item {Modeling, analysis, and manufacture of a vehicle-based RIN.}
        \item {Elaboration of processes sheets, strain simulation and post-processing of the manufacturing operations.}
        \item {Design and development of mobile robots using 3D printing and laser cutting techniques.}
      \end{cvitems}
    }

  % \cventry
  %   {Army Forces University - ESPE}
  %   {Undergraduate Researcher, Manufacturing Processes Lab.}
  %   {Quito, Ecuador.}
  %   {Jan. 2015 - Mar. 2015}
  %   {
  %     \begin{cvitems}
  %       \item {Design and development of mobile robots using 3D printing and laser cutting techniques.}
  %     \end{cvitems}
  %   }

\end{cventries}
