%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-emerald}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./photo}
\name{Guido}{ Santillán}
\position{Full-Stack Web Developer{\enskip\cdotp\enskip}Mechatronics Engineer{\enskip\cdotp\enskip}Tech enthusiast}
\address{N71-38 John F. Kennedy, Pablo Picasso, Quito, 170301, Ecuador}

\mobile{(+593) 98 747 3691 GMT-5} 
\email{info@guidosantillan.com}
\homepage{www.guidosantillan.com}
\github{guidosantillan01}
\linkedin{guido92}
\xing{Guido\_Santillan}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \extrainfo{extra informations}

% \quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Company Recruitment Team}
  {On-apply GmbH.\\Solmsstraße 83\\60486 Frankfurt am Main}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Full Stack Developer}
% How the letter is opened
\letteropening{Dear Hiring Manager,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[C]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Guido Santillán~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

With hands-on experience developing web applications using React, Redux, NodeJS, Express, and PostgreSQL, I offer the technical expertise On-apply is seeking for its full-stack developer position posted on StackOverflow. 

\lettersection{About Me}
I'm a skillful full-stack developer experienced in all stages of the software development cycle. Good understanding of web-related technologies such as HTML, CSS, SCSS, Javascript, ES6, Git, REST, build tools, Netlify, and Heroku for hosting. For the past 2 years, I have also been helping companies improve their online presence by designing and building their websites. Always taking into account good development practices, mobile-friendly support, and solid digital marketing strategies such as SEO and email marketing to increase visitor traffic and to further reach current clients.

In addition to that, I have a bachelor's degree in Mechatronics Engineering from one of the most respected universities in my country, was part of a group of selected students who traveled to Germany to do academic research and had a fulfilling experience implementing machine learning and deep learning in various projects during an online scholarship hosted by Udacity and Facebook.

\lettersection{Why Me?}
As a fast learner and hard-working individual who adapts quickly to assess an organization’s needs, I firmly believe my skills will make a significant contribution to On-apply's strengths. I am actively looking forward to expanding my knowledge, improve my abilities and obtain relevant experience in the industry in order to help create world-changing solutions. 

I'd be thrilled to learn more about the full-stack developer position. If my skills match your requirements or you want to know more about me, please do not hesitate to contact me at \href{mailto:info@guidosantillan.com}{info@guidosantillan.com}. I am grateful to you for the time taken reviewing my application.

\end{cvletter}

%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

P.S. — Perhaps we could also schedule a video call via Skype if you find it suitable. I am excited to show you how I can help On-apply's mission to make application processes easier and more efficient. 

P.P.S. —  I am currently living in Quito-Ecuador but I will be moving to Germany in the next month.

\end{document}
