%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-skyblue}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./photo}
\name{Guido}{Santillan}
\address{Hausotterstr. 21, 13409 Berlin, Germany}
\mobile{(+49) 176 3522 8977 CEST}

\position{Full-Stack Web Developer{\enskip\cdotp\enskip}Mechatronics Engineer{\enskip\cdotp\enskip}Tech enthusiast}

\email{info@guidosantillan.com}
\homepage{www.guidosantillan.com}
\github{guidosantillan01}
\linkedin{guido92}
\xing{Guido\_Santillan}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \extrainfo{extra informations}

% \quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {[COMPANY_NAME] HR Team}
  % {[COMPANY_NAME] GmbH\\Berlin, Germany}
  {[COMPANY_NAME] GmbH\\Zossener Str. 55\\10961 Berlin, Germany}

% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for [JOB POSITION]}
% How the letter is opened
% Dear Hiring Manager
\letteropening{Dear Hiring Manager,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[C]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Guido Santillan~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

With hands-on experience developing web applications using modern technologies, and as a holder of a bachelor's degree in Mechatronics Engineering, I offer the technical expertise [COMPANY_NAME] is seeking for its [JOB POSITION] position posted on [StackOverflow].

\lettersection{About Me}
I'm a junior full-stack developer experienced in all stages of the software development cycle. Good understanding of web-related technologies such as HTML5, CSS3, Javascript, React, NodeJS, REST API, version control, GitHub, Docker, databases, PostgreSQL, MongoDB, build tools, CI/CD, testing and deploying.

In addition to that, I hold a bachelor's degree in Mechatronics Engineering from one of the most respected universities in my country. During my studies, I completed projects on various topics, going from Robotics and Automation to Electronics and IoT. For that, I have used multiple programming languages and tools such as C, C++, Python, Matlab, Simulink, LabVIEW, Solidworks.

The automotive industry has always fascinated me; I even developed my bachelor's thesis project in that field. I was part of a group of selected students who travelled to Germany to do academic research. This thesis project took place in Technische Hochschule Brandenburg, and its fundamental objective was to provide an effective platform for development, testing, and validation of different electronic car components like electronic control units (ECU) and other embedded real-time systems.

\lettersection{Why Me?}
As a fast learner and hard-working individual, I firmly believe my skills will make a significant contribution to [COMPANY_NAME]'s strengths. I use my interdisciplinary thinking and creativity to adapt quickly to assess an organization's needs. I am actively looking forward to expanding my knowledge, improve my abilities, and obtain relevant experience in the industry to help develop world-changing solutions.

I'd be thrilled to learn more about the [JOB POSITION] position. I am immediately available for the job, and my salary expectations are negotiable. If my skills match your requirements or you want to know more about me, please do not hesitate to contact me at info@guidosantillan.com. I am grateful to you for the time taken reviewing my application.

\end{cvletter}

%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

P.S. — I have attached my resume for your consideration.

P.S.S. — Perhaps we could also schedule a video call if you find it suitable. I am excited to show you how I can help [COMPANY_NAME] 's mission to [develop world-changing solutions].

\end{document}
