%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-skyblue}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./photo}
\name{Guido}{ Santillán}
\position{Full-Stack Web Developer{\enskip\cdotp\enskip}Mechatronics Engineer{\enskip\cdotp\enskip}Tech enthusiast}
\address{N71-38 John F. Kennedy, Pablo Picasso, Quito, 170301, Ecuador}

\mobile{(+593) 98 747 3691 GMT-5}
\email{info@guidosantillan.com}
\homepage{www.guidosantillan.com}
\github{guidosantillan01}
\linkedin{guido92}
\xing{Guido\_Santillan}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \extrainfo{extra informations}

% \quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Medici Living Group HR Team}
  % {Medici Living Group GmbH\\Berlin, Germany}
  {Medici Living Group GmbH\\Zossener Str. 55\\10961 Berlin, Germany}

% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Javascript Developer}
% How the letter is opened
% Dear Hiring Manager
\letteropening{Dear Hiring Manager,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[C]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Guido Santillán~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

With hands-on experience developing web applications using React, Redux, NodeJS, Express, and PostgreSQL, I offer the technical expertise Medici Living Group is seeking for its Javascript Developer position.

\lettersection{About Me}
I'm a mid-level full-stack developer experienced in all stages of the software development cycle. Good understanding of web-related technologies such as HTML, CSS, Javascript, REST, npm, version control, build tools, Webpack, Docker, testing and deploying. For the past two years, I have also been helping companies improve their online presence by designing and building their websites, always taking into account good development practices, mobile-friendly support, and reliable digital marketing strategies such as SEO and email marketing to increase visitor traffic and to further reach current clients.

In addition to that, I have a bachelor's degree in Mechatronics Engineering from one of the most respected universities in my country. I was part of a group of selected students who traveled to Germany to do academic research and had a fulfilling experience implementing machine learning and deep learning in various projects during an online scholarship hosted by Udacity and Facebook.

\lettersection{Why Me?}
As a fast learner and hard-working individual who adapts quickly to assess an organization's needs, I firmly believe my skills will make a significant contribution to Medici Living Group's strengths. I am actively looking forward to expanding my knowledge, improve my abilities, and obtain relevant experience in the industry to help create world-changing solutions.

I'd be thrilled to learn more about the Javascript developer position. If my skills match your requirements or you want to know more about me, please do not hesitate to contact me at \href{mailto:info@guidosantillan.com}{info@guidosantillan.com}. I am grateful to you for the time taken reviewing my application.

\end{cvletter}

%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

P.S. — Perhaps we could also schedule a video call via Skype if you find it suitable. I am excited to show you how I can help reach Medici Living Group's vision of developing innovative and tech-enabled rental housing solutions.

P.P.S. —  I am currently living in Quito-Ecuador, and I will be moving to Berlin in the next days.

\end{document}
