\cvsection{Experience}

\begin{cventries}

  \cventry
    {Independent}
    {Web Developer}
    {Quito, Ecuador}
    {April 2018 - Current}
    {
      \begin{cvitems}
        \item {Redesign of \href{https://aefran.org}{Asociacion Ecuatoriana de Franquicias} website.}
        \item {Redesign of \href{http://www.ecuafranquicias.com}{Ecuafranquicias} website.}
        \item {Redesign of \href{http://www.villagranlara.com}{Villagran Lara Asociados} website.}                       
      \end{cvitems} 
    }
    
  \cventry
    {Ecuafranquicias}
    {Project Manager}
    {Quito, Ecuador.}
    {June 2017 - April 2019}
    {
      \begin{cvitems}
        \item {Franchisable business's operative and administrative processes documentation and management.}
        \item {Part-time job based-on time availability.}
      \end{cvitems}
    }

  \cventry
    {Department of Energy and Mechanic Sciences - ESPE}
    {Research and Teaching Assistant of: Computer-aided Design, Manufacture and Engineering subject (CAD, CAM, CAE)	}
    {Quito, Ecuador}
    {Nov. 2015 – Mar. 2016}
    {
      \begin{cvitems}
        \item {Modelling, analysis and manufacture of a vehicle-based RIN. }
        \item {Out-come report generation, elaboration of processes sheets, G-code programming, design of the vehicle-based RIN using computer-aided software, strain simulation and post-process of the manufacturing operations.}
      \end{cvitems}
    }
  
  \cventry
    {Army Forces University - ESPE}
    {Undergraduate Researcher, Manufacturing Processes Lab.}
    {Quito, Ecuador.}
    {Jan. 2015 - Mar. 2015}
    {
      \begin{cvitems}
        \item {Design and development mechanism for mobile robots mechanisms using 3D printing and laser cutting techniques.}
      \end{cvitems}
    }
        
\end{cventries}
