\cvsection{Experience}

\begin{cventries}

  \cventry
    {Ecuafranquicias}
    {Project Manager}
    {Quito, Ecuador}
    {April 2017 - April 2019}
    {
      \begin{cvitems}
        \item {Automation of multiple internal processes using oﬀice automation tools and Excel to reduce in half the time needed to deliver the product to our clients while simultaneously detecting errors in the development stage and giving employees more autonomy to develop their daily tasks.}
        \item {While the processes automation improved a lot of things, it was not enough to maximize the performance of the employees. A system was needed. The development of a tool was pitched to solve these problems, this tool will use modern technologies to gather, store, and manage information in an accessible way for our employees.}
        \item {Operative and administrative process documentation of our clients.}
        \item {Implementation of email marketing campaigns using MailChimp to approximately 3000+ subscribers.}
        \item {An SEO strategy was put in place to improve local search results. This strategy consisted of webpage redesign, webpage optimization, keyword research and analysis, content creation, webpage analytics.}
      \end{cvitems}
    }

    \cventry
      {Independent Work}
      {Web Developer}
      {Quito, Ecuador}
      {June 2017 - June 2018}
      {
        \begin{cvitems}
          \item {Redesign of multiple websites, including \href{https://aefran.org}{\textit{Asociación Ecuatoriana de Franquicias}}, \href{http://www.ecuafranquicias.com}{\textit{Ecuafranquicias}}, \href{http://www.villagranlara.com}{\textit{Villagran Lara Asociados}} using various CMS.}
          \item {Websites were designed with a focus on achieving maximum performance, faster loading times, mobile-friendly and optimized for SEO purposes.}                       
        \end{cvitems} 
      }

  \cventry
    {Department of Energy and Mechanic Sciences - ESPE}
    {Research and Teaching Assistant of Computer-aided Design, Manufacture and Engineering subject (CAD, CAM, CAE)	}
    {Quito, Ecuador}
    {Nov. 2015 – Mar. 2016}
    {
      \begin{cvitems}
        \item {Modeling, analysis, and manufacture of a vehicle-based RIN.}
        \item {Out-come report generation, elaboration of processes sheets, G-code programming, design of the vehicle-based RIN using computer-aided software, strain simulation and post-process of the manufacturing operations.}
      \end{cvitems}
    }
  
  \cventry
    {Army Forces University - ESPE}
    {Undergraduate Researcher, Manufacturing Processes Lab.}
    {Quito, Ecuador.}
    {Jan. 2015 - Mar. 2015}
    {
      \begin{cvitems}
        \item {Design and development of mobile robots using 3D printing and laser cutting techniques.}
      \end{cvitems}
    }
        
\end{cventries}
